Predr_Cors

### 2023-10-21 Markdown/Manuscript/Child_RMDs/MS_Discussion.Rmd
one table to go

<!-- Talk about DARTH (https://doi.org/10.1007/s40273-019-00837-x )/ BCEA -->
Ethical practice is a core expectation of health researchers and computational methods underpin most quantitative research, yet an understanding of what constitutes ethical public health modelling practice is underdeveloped [@10.3389/fpubh.2017.00068]. We have addressed this gap with our proposed project team responsibilities, enabling model attributes and model implementation assessment criteria.

@@

As illustrated by Table \@ref(tab:checktb), we have developed a prototype software framework that can be used to implement youth mental health CHEMs that largely satisfy our TRU criteria. However, in its current form our software framework is too fragile to be recommended as anything more than a prototype for supporting the development needs of other modelling teams and projects. We developed our prototype software framework primarily to address the user requirements of one group – ourselves. Factors such as user enjoyment, usability, active user-community and supporting resources influence adoption of software frameworks [@myllarniemi2018development]. We currently lack the resources required to provide ongoing address these issues.

However, our prototype has a number of features that future work on CHEM software frameworks may find useful to incorporate. Firstly, developing a software framework to work within an existing and widely used open source programming language such as R or python, can keep framework scope relatively narrow. This makes it more tractable to develop, maintain and learn, and can integrate other modelling tools written in that language (e.g., the dependency libraries we list in Table \@ref(tab:cpkgs)). Secondly, implementation that combines both object-oriented and functional programming paradigms can avail of the modular and syntactical simplicity benefits of the former, while limiting needless bundling of code artefacts. Thirdly, a sensible trade-off needs to be found between transparent code implementation (which requires clear and sufficiently detailed documentation) and Agile Software Development (for which a foundational principle is prioritising the development of working code over writing documentation [@beck2001manifesto]). Our software framework makes this trade off by enforcing the use of consistent naming conventions and file organisation which in turn enables automated generation of simple documentation at every code update. All model data-structures and algorithms are therefore always documented (at least minimally, with machine authored content), meaning model developers have a requirement to write customised documentation less frequently. Many of the features of our prototype software framework have the potential to be significantly enhanced through integration with evolving code-authoring and documentation authoring capabilities of large language models.

Our software framework provides the outline of a technical solution to some of the challenges of open source CHEM development. However, better tools alone are insufficient and policy and institutional changes are also required. Reducing waste in research is a core responsibility of research funders [@chalmers2014increase] and funding the development of CHEMs that are not adequately understood, reused or updated is wasteful. Existing incentive structures for health economists generally do not promote facilitating peers to reuse their work and funding is rarely adequate to maintain an routinely update a model. Currently, it can take “an extraordinary amount of idealism” to commit to authoring and maintaining research software [@anzt2020environment]. Previously recommended strategies for more beneficial health economic research investments include support for harmonised ethical standards for model development [@10.3389/fpubh.2017.00068], methodological innovation to improve model transferability [@craig2018taking], networks of modellers working on common health conditions [@Sampson2019], and  centralized infrastructure such as open source model repositories [@Pouwels2022] and a standard platform for model implementations [@Ghabri2019]. Development of software frameworks to support ethical CHEM implementations could enable and enhance each of these strategies.

A future software framework for ethical CHEMs would ideally incorporate a base set of features useful to developers of computational models across all domains of public health, with the capability for community-led extensions that are tailored to the needs of modellers focused on specific health-conditions. Such approaches will likely be important to ensure that the potential user-base is sufficient to make CHEM software frameworks sustainable.

>>>>

<!-- Talk about DARTH (https://doi.org/10.1007/s40273-019-00837-x )/ BCEA -->
Ethical practice is a core expectation of health researchers and computational methods underpin most quantitative research, yet an understanding of what constitutes ethical public health modelling practice is underdeveloped [@10.3389/fpubh.2017.00068]. We have addressed this gap with our proposed responsibilities for model developers and funders, enabling CHEM attributes and CHEM implementation assessment criteria.

@@

As illustrated by Table \@ref(tab:checktb), we have developed a prototype software framework that can be used to implement youth mental health CHEMs that largely satisfy our TRU criteria. However, in its current form our software framework is too fragile to be recommended as anything more than a prototype for supporting the development needs of other modelling teams and projects. We developed our prototype software framework primarily to address the user requirements of one group – ourselves. Factors such as user enjoyment, usability, active user-community and supporting resources influence adoption of software frameworks [@myllarniemi2018development]. We currently lack the resources required to  address these issues for our software framework.

However, our prototype has a number of features that future work on CHEM software frameworks may find useful to incorporate. Firstly, developing a software framework to work within an existing and widely used open source programming language such as R or Python, can keep framework scope relatively narrow. This makes it more tractable to develop, maintain and learn, and can integrate other modelling tools written in that language (e.g., the dependency libraries we list in Table \@ref(tab:cpkgs)). Secondly, implementation that combines both object-oriented and functional programming paradigms can avail of the modular and syntactical simplicity benefits of the former, while limiting needless bundling of code artefacts. Thirdly, a sensible trade-off needs to be found between transparent code implementation (which requires clear and sufficiently detailed documentation) and Agile Software Development (for which a foundational principle is prioritising the development of working code over writing documentation [@beck2001manifesto]). Our software framework makes this trade off by enforcing the use of consistent code style conventions and file organisation which in turn enables automated generation of simple documentation at every CHEM module update. All model data-structures and algorithms are therefore always documented (at least minimally, with machine authored content), meaning model developers have a requirement to write customised documentation less frequently. Many of the features of our prototype software framework have the potential to be significantly enhanced through integration with evolving code and documentation authoring capabilities of large language models.

Our software framework provides the outline of a technical solution to some of the challenges of open source CHEM development. However, better tools alone are insufficient and policy and institutional changes are also required. Reducing waste in research is a core responsibility of research funders [@chalmers2014increase] and funding the development of CHEMs that are not adequately understood, reused or updated is wasteful. Existing incentive structures for health economists generally do not promote facilitating peers to reuse their work and funding is rarely adequate to maintain and routinely update a model. Currently, it can take “an extraordinary amount of idealism” to commit to authoring and maintaining research software [@anzt2020environment]. Previously recommended strategies for more beneficial health economic research investments include support for harmonised ethical standards for model development [@10.3389/fpubh.2017.00068], methodological innovation to improve model transferability [@craig2018taking], networks of modellers working on common health conditions [@Sampson2019], and  centralized infrastructure such as open source model repositories [@Pouwels2022] and a standard platform for model implementations [@Ghabri2019]. Development of software frameworks to support ethical CHEM implementations could enable and enhance each of these strategies.

A future software framework for ethical CHEMs would ideally incorporate a base set of features useful to developers of computational models across all domains of public health and health economics, with the capability for community-led extensions that are tailored to the needs of modellers focused on specific health-conditions. Such approaches will likely be important to ensure a sufficient potential user-base to make CHEM software frameworks sustainable.

### 2023-10-21 Markdown/Manuscript/Child_RMDs/MS_Imp_Example.Rmd
one table to go

Although we are principally interested in using CHEMs to answer policy questions relating to the mental health of young people in Australia, we want to facilitate CHEM transferability to other jurisdictions. Our CHEMs are being derived from and applied to real data (which can be assumption, empirical or simulated, so long as it is appropriate for use in analysis intended to inform decision-making) from Australia. To help demonstrate the potential use of CHEMs in other decision contexts, we also create toy datasets. Data created for illustration purposes is prominently labelled as not for use in decision-analysis.

@@

 - collections of real data (study input and results [@DVN/DKDIB0_2021]) and fake data (synthetic populations for testing model modules [@DVN/HJXYKQ_2021]);

>>>>

Although we are principally interested in using CHEMs to answer policy questions relating to the mental health of young people in Australia, we want to facilitate CHEM transferability to other jurisdictions. Our CHEMs are being derived from and applied to real data (which can be empirical, simulated or assumption, so long as it is appropriate for use in analysis intended to inform decision-making) from Australia. To help demonstrate the potential use of CHEMs in other decision contexts, we also create toy datasets. Data created for illustration purposes is prominently labelled as not for use in decision-analysis.

@@

 - collections of real data (study input and results [@DVN/DKDIB0_2021]) and toy data (synthetic populations for testing model modules [@DVN/HJXYKQ_2021]);

### 2023-10-21 Markdown/Manuscript/Child_RMDs/MS_Imp_Guidelines.Rmd
one table to go

We considered prior literature on modelling practice and our own experience with developing and using CHEMs to identify: (i) some core ethical responsibilities of CHEM project teams; (ii) attributes of CHEMs that can suggest fulfillment of these responsibilities; and (iii) criteria against which these attributes can be assessed.

@@

To help identify ethical responsibilities that are specific to CHEM project teams, we first considered the distinct phases in a software development project. Software development lifecycle (SDLC) models take different approaches to the inclusion, naming, definition, sequencing and iteration of project phases [@ruparelia2010software]. However, SDLC models typically have components that can principally map to the concepts of *planning* (e.g., identification of system / user requirements and design specifications), *implementation* (e.g., development and testing) and *release* (e.g., deployment, system integration, maintenance and support). For simplicity, we propose one overarching ethical responsibility for CHEM developers and funders for each of these phases. These responsibilities are to:

(i) **establish socially acceptable system requirements and design specifications** (during CHEM planning);

(ii) **ensure fit for purpose implementation** (during CHEM implementation); and

@@

Each responsibility relates to aspects of Boden and McKendrick's ethical criteria. Transparency underpins all three responsibilities (Table \@ref(tab:timelygls). Additionally, the planning responsibility incorporates justice and independence, the implementation responsibility incorporates independence and the release responsibility incorporates beneficence / non-maleficence and justice. All three ethical responsibilities have implications for both professional practice and project resourcing and should therefore apply to model developers and funders jointly.

@@

Misalignment between the values of computational model developers and those of the population groups affected by decisions based on their models presents significant ethical risks [@thompson2022escape; @duckett2022journey].  The value judgments of health economic modellers are rarely adequately specified, omissions that may lead to socially unacceptable policy recommendations [@duckett2022journey]. These value judgments influence the assumptions, selection of model features and standards for evidence that shape health economic model projects [@HARVARD2020112975]. For example, as illustrated in Table \@ref(tab:proscons), project resource constraints may require trade-offs between desired CHEM **system requirements and design** features. These trade-offs in turn determine how straightforward it is for CHEMs to be amended by third parties to reflect alternative value judgments in model conceptualisation and mathematical formalisation (Table \@ref(tab:timelygls)).

@@

A CHEM that is **reusable** also signals ethical modelling practice. Making a CHEM’s code, data and documentation publicly available is increasingly considered good practice, yet is not sufficient to promote model re-use.  Key concepts in health economic model reuse include generalisability (application without adaptation) and transferability (selective reuse and/or modification of model components) [@RN39]. Writing model algorithms as collections of functions (short, self-contained and reusable software routines that each perform a discrete task) is good scientific computing practice [@Wilson_2017] and promotes selective reuse. Computational implementations that store model code and data in distinct files and locations (as opposed to embedding data such as parameter values into source code) are easier to selectively modify. Modular implementations construct models from multiple independently reusable and replaceable sub-models (modules) [@pan2021modular]. The programming concept inheritance [@8717448], deployed in object-oriented programming approaches, can facilitate the duplication and selective modification of models. Granting permissions to others to use, test and adapt models and their components, can be facilitated by two broad categories of open source licenses. Some guidance strongly recommends the use of permissive licensing [@Wilson_2017] that provides users with great flexibility as to the purposes (including commercial) for which content can be re-used. An alternative approach is to use copyleft licenses [@copyleft2022] that can require content users to distribute any derivative works they create under similar open-source arrangements. 
<!-- Compared to using commercial modelling software, authoring CHEMs in an open-source language like R [@RCORE2022] makes it easier to -->
<!-- Using open-source development platforms and licenses can aid both generalizability and transferability. -->
<!-- The choices that CHEM developers make about model implementation and licensing will also shape who can use a model and for what purposes.  -->
<!-- are relatively easier to selectively modify. -->

@@

-	**R2**: Terms of use place restrict only unethical usage and allow anyone to ethically reuse model code and non-confidential data, in whole or in part, without charge, and for purposes that include the creation of derivative works.

>>>>

We considered literature on modelling practice and reflected on our prior experience with developing and using CHEMs to identify: (i) some core ethical responsibilities of CHEM project teams; (ii) attributes of CHEMs that can suggest fulfillment of these responsibilities; and (iii) criteria against which these attributes can be assessed.

@@

To identify ethical issues that are specific to CHEMs, we first considered the distinct phases in a software development project. Software development lifecycle (SDLC) models take different approaches to the inclusion, naming, definition, sequencing and iteration of project phases [@ruparelia2010software]. However, SDLC models typically have components that can principally map to the concepts of *planning* (e.g., identification of system / user requirements and design specifications), *implementation* (e.g., development and testing) and *release* (e.g., deployment, system integration, maintenance and support). For simplicity, we propose one overarching ethical responsibility for CHEM project teams for each phase. These responsibilities are to:

(i) **establish socially acceptable user requirements and design specifications** (during CHEM planning);

(ii) **ensure fitness for purpose** (of CHEM implementation); and

@@

Transparency underpins all three responsibilities (Table \@ref(tab:timelygls)). Boden and McKendrick’s other ethical criteria can be selectively mapped to each phase's responsibility: justice and independence to the planning responsibility; independence to the implementation responsibility; and beneficence / non-maleficence and justice to the release responsibility. All three ethical responsibilities have implications for both professional practice and project resourcing. As it is unreasonable to place expectations of modellers that they are not resourced to fulfil, these responsibilities should apply jointly to health economic model developers and funders.

@@

Misalignment between the values of computational model developers and those of the population groups affected by decisions based on their models presents significant ethical risks [@thompson2022escape; @duckett2022journey].  The value judgments of health economic modellers are rarely adequately specified, omissions that may lead to socially unacceptable policy recommendations [@duckett2022journey]. These value judgments influence the assumptions, selection of model features and standards for evidence that shape health economic model projects [@HARVARD2020112975]. For example, as illustrated in Table \@ref(tab:proscons), project resource constraints may require model developers to make trade-offs when agreeing CHEM **user requirements and design specifications**. These trade-offs in turn determine how straightforward it is for a CHEM to be subsequently amended to reflect alternative value judgments relating to model conceptualisation and mathematical formalisation (Table \@ref(tab:timelygls)).

@@

A CHEM that is **reusable** also signals ethical modelling practice. Although making a CHEM’s code, data and documentation publicly available is increasingly considered good practice, it is insufficient to enable model re-use.  Key concerns for health economists when considering model reuse are generalisability (application without adaptation) and transferability (selective reuse and/or modification of model components) [@RN39]. Writing model algorithms as collections of functions (short, self-contained and reusable software routines that each perform a discrete task) is good scientific computing practice [@Wilson_2017] and promotes selective reuse. Computational implementations that store model code and data in distinct files and locations (as opposed to embedding data such as parameter values into source code) are easier to selectively modify. Modular implementations construct models from multiple independently reusable and replaceable sub-models (modules) [@pan2021modular]. The programming concept inheritance [@8717448], deployed in object-oriented programming approaches, can facilitate the duplication and selective modification of models. Granting permissions to others to use, test and adapt models and their components, can be facilitated by two broad categories of open source licenses. Some guidance strongly recommends the use of permissive licensing [@Wilson_2017] that provides users with great flexibility as to the purposes (including commercial) for which content can be re-used. Alternatively, copyleft licenses [@copyleft2022] can be used to require that derivative works created by content users remain open-source. 
<!-- Compared to using commercial modelling software, authoring CHEMs in an open-source language like R [@RCORE2022] makes it easier to -->
<!-- Using open-source development platforms and licenses can aid both generalizability and transferability. -->
<!-- The choices that CHEM developers make about model implementation and licensing will also shape who can use a model and for what purposes.  -->
<!-- are relatively easier to selectively modify. -->

@@

-	**R2**: Licenses restrict only unethical use and allow anyone to ethically reuse model code and non-confidential data, in whole or in part, without charge, and for purposes that include the creation of derivative works.

### 2023-10-21 Markdown/Manuscript/Child_RMDs/MS_Imp_Toolkit.Rmd
one table to go

A library for **managing CHEM data** contains tools for supplying CHEM modules with input data ingested from local (i.e., a user's computer) or remote (online repositories) locations, labelling CHEM module datasets and exporting CHEM module data to online repositories. A library for **authoring reproducible analyses** contains tools to help write programs that apply CHEM modules to compatible datasets for the purpose of undertaking health economic analyses. These analysis programs can be either self-documenting (code is integrated with plain English explanations of what it does) or trigger the creation of separate documents (e.g., a scientific manuscript).

@@

##	Documentation website
We developed a framework documentation website (www.ready4-dev.com) that provides guidance to model developers on how to use and contribute improvements to the ready4 software framework and models developed with it. The documentation website is versioned, which means documentation relating to prior versions of framework software can be archived, retrieved and viewed.

>>>>

A library for **managing CHEM data** contains tools for supplying CHEM modules with input data ingested from local (i.e., a user's computer) or remote (online repositories) locations, labelling CHEM module datasets and exporting CHEM module data to online repositories. A library for **authoring reproducible analyses** contains tools to help write programs that apply CHEM modules to compatible datasets for the purpose of undertaking health economic analyses. These analysis programs can be either self-documenting (code is integrated with plain English explanations of what it does) or trigger the creation of explanatory documents (e.g., a scientific manuscript).

@@

##	Documentation website
We developed a framework documentation website (https://www.ready4-dev.com) that provides guidance to model developers on how to use and contribute improvements to the ready4 software framework and CHEM modules developed with it. The documentation website is versioned, which means documentation relating to prior versions of framework software can be archived, retrieved and viewed.

### 2023-10-21 Markdown/Manuscript/Child_RMDs/MS_Tables_3.Rmd
one table to go

---
title: "Predr_Cors"
author: "Author"
date: "`r Sys.Date()`"
output: html_document
---
```{r cpkgs, tab.cap='Software framework R libraries', tab.id = 'cpkgs', echo = F, results = 'asis'}
library(kableExtra)  
df <- tibble::tibble(Package = c("ready4",
                                       "ready4fun",
                                       "ready4class",
                                       "ready4pack",
                                       "ready4use",
                                       "ready4show"),
                           # Version = Package %>%
                           #   purrr::map_chr(~utils::packageDescription(.x) %>%
                           #                    purrr::pluck("Version")),
                           Focus = c("Foundation",
                                     "Module algorithms",
                                     "Module structures",
                                     "Module libraries",
                                     "Datasets",
                                     "Analyses"),
                           A = c("3","2-3","2","1-2,5,7","1-2,7","4,6"), 
                           R = c("4","5","4-5","1,3,6","3,7",""),
                           U = c("","","","1-3","1",""),
                           # E = c("", "1","1-2","1","3",""),
                           # L = c("","","","1,3","2-3",""),
                           # Y = c("","","","","","1-2"),
                           `Depends on` = Package %>%
                             purrr::map(~ {
                               utils::packageDescription(.x) %>%
                                 `[`(c("Depends", "Imports")) %>%
                                 purrr::map(~{
                                   if(is.null(.x)){
                                     character(0)
                                     }else{
                                       .x %>%
                                         strsplit(",\\n") %>%
                                         purrr::flatten_chr() %>%
                                         purrr::map(~strsplit(.x,", ") %>%
                                                      purrr::flatten_chr()) %>%
                                         purrr::flatten_chr() %>% sort() %>%
                                         purrr::discard(~startsWith(.x,"R "))
                                       }
                                   }) %>%
                                 purrr::flatten_chr() %>%
                                 unique() %>%
                                 sort() %>%
                                 purrr::map_chr(~{
                                   updated_1L_chr <- stringr::str_replace_all(.x,"\\n"," ")
                                   problem_idx_1L_chr <- stringr::str_locate(updated_1L_chr," ")[1,1] %>%
                                     unname()
                                   if(!is.na(problem_idx_1L_chr))
                                     updated_1L_chr <- updated_1L_chr %>%
                                     stringr::str_sub(end = problem_idx_1L_chr-1)
                                   updated_1L_chr %>% 
                                     trimws(which = "left") 
                                   })
                               }) %>% 
                             purrr::map_chr (~ .x %>% paste0(collapse = " "))) %>% 
  as.data.frame() 
if(params$X@outp_formats_chr[1] != "Word"){
      df$Ref <- c(rep("",6)
       # "@ready42022","@ready4fun2022","@ready4class2022","@ready4pack2022","@ready4use2022","@ready4show2022"
                  )
}else{
  df$Ref <- ""
}

df <- df %>%
  dplyr::mutate(Standard = purrr::pmap_chr(df,
                                           ~paste0("A",
                                                  ..3,
                                                  paste0(rep("&nbsp;",
                                                      2+max(nchar(df[,3]))-nchar(..3)),
                                                      collapse = ""#
                                                      ),
                                                  ifelse(..4=="","","R"),
                                                  ..4,
                                                  paste0(rep("&nbsp;",
                                                      2+max(nchar(df[,4]))-nchar(..4)),
                                                      collapse = ""#
                                                      ),
                                                  ifelse(..5=="","","U"),
                                                  ..5,
                                                  paste0(rep("&nbsp;",
                                                      1+max(nchar(df[,5]))-nchar(..5)),
                                                      collapse = ""#
                                                      )#,
                                                  # ifelse(..6=="","","E"),
                                                  # ..6,
                                                  # paste0(rep("&nbsp;",
                                                  #     1+max(nchar(df[,6]))-nchar(..6)),
                                                  #     collapse = ""#
                                                  #     ),
                                                  # ifelse(..7=="","","L"),
                                                  # ..7,
                                                  # # paste0(rep("&nbsp;",
                                                  # #     1+max(nchar(df[,7]))-nchar(..7)),
                                                  # #     collapse = ""#
                                                  # #     ),
                                                  # ifelse(..8=="","","&nbsp; &nbsp; &nbsp; &nbsp; Y"),
                                                  # ..8,
                                                  # paste0(rep("&nbsp;",
                                                  #     1+max(nchar(df[,8]))-nchar(..8)),
                                                  #     collapse = ""#
                                                  #     )
                                                  ))) %>%

  dplyr::select(Package,
                Ref,
                Focus,
                Standard,
                `Depends on`)

names_chr <- names(df)
df <- data.frame(df[,1],
                 rep(ifelse(params$X@outp_formats_chr[1] == "Word"," ","&nbsp; &nbsp; &nbsp;"),
                     nrow(df)),
                 df[,2:3],
                 rep(ifelse(params$X@outp_formats_chr[1] == "Word"," ","&nbsp; &nbsp; &nbsp;")
                     ,nrow(df)),
                 df[,4],
                 #rep("&nbsp; &nbsp; &nbsp;",nrow(df)),
                 df[,5])
colnames(df) <- c("Package",
                  ifelse(params$X@outp_formats_chr[1] == "Word","XXX"," "),
                  "Ref", "Focus", 
                  ifelse(params$X@outp_formats_chr[1] == "Word","YYY"," "),
                  "Standard     ",# " ",
                  "Depends on these R libraries")
#df$Package <- "![](../Data/images/ready4.png){ width=10% }"#"\\includegraphics[valign=T,scale=2.5,raise=2mm]{../Data/images/ready4.png}"
df$`Standard     `  <- df$`Standard     ` %>% stringr::str_replace_all("&nbsp;"," ")
if(params$X@outp_formats_chr[1] == "Word") {
  library("flextable")
  library("ftExtra")
  df[,c(1,3:4,6:7)] %>%
    ready4show::print_table(output_type_1L_chr = params$X@outp_formats_chr[1],
                            caption_1L_chr = knitr::opts_current$get("tab.cap"),
                            mkdn_tbl_ref_1L_chr = paste0("tab:",knitr::opts_current$get("tab.id")),
                            use_rdocx_1L_lgl = ifelse(params$X@outp_formats_chr[1]=="Word",T,F),
                            add_to_row_ls = NULL,
                            sanitize_fn = NULL) %>%
    ftExtra::colformat_md()
  }else{
    df$Ref<-NULL
    #df$Package <- ""
    df$Package  <- df$Package %>% 
                      purrr::map_chr(~paste0("\\includegraphics[valign=M,width=1.9cm,raise=4mm]{../Data/images/",.x,"_logo.png}"))#scale=0.4,raise=3mm]
    # df$Package <- "\\includegraphics[valign=M,scale=0.08,raise=3mm]{../Data/images/ready4.png}"
    df[,c(1,3,5:6)]   %>%
    # kableExtra::kbl(format = "markdown",
    #                   escape = F,
    #                 caption = knitr::opts_current$get("tab.cap"))
      kableExtra::kbl(booktabs = T, 
                      escape = F,
                      caption = knitr::opts_current$get("tab.cap")) %>%
      kableExtra::kable_paper(full_width = F) %>%
      kableExtra::column_spec(3,latex_valign = "m") %>%
      # kableExtra::column_spec(1, 
      #                         image = kableExtra::spec_image(rep("../Data/images/ready4.png",nrow(df)), 
      #                                                           150, 150)) %>%
      kableExtra::column_spec(4, width = "24em",latex_valign = "m")
    }
```

>>>>

---
title: "Predr_Cors"
author: "Author"
date: "`r Sys.Date()`"
output: html_document
---
```{r cpkgs, tab.cap='Software framework R libraries', tab.id = 'cpkgs', echo = F, results = 'asis'}
library(kableExtra)  
df <- tibble::tibble(Package = c("ready4",
                                       "ready4fun",
                                       "ready4class",
                                       "ready4pack",
                                       "ready4use",
                                       "ready4show"),
                     Purpose = c("Provide a template and novel syntax for modular CHEM implementations and tools for finding interoperable CHEM modules, datasets and reproducible analysis programs.",
                                 "Streamline and standardise the authoring and documenting of functions that support transferable and generalisable model algorithms.",
                                 "Streamline and standardise the authoring and documenting of new interoperable CHEM modules.",
                                 "Help bundle and disseminate newly created CHEM modules as R libraries that are documented, licensed and quality assured.",
                                 "Help manage the labelling and transfer of data between CHEM modules and local and remote data repositories.",
                                 "Facilitate the use of CHEM modules in programs to implement integrated and reproducible data ingest, analysis and reporting pipelines."),
                           # A = c("3","2-3","2","1-2,5,7","1-2,7","4,6"), 
                           # R = c("4","5","4-5","1,3,6","3,7",""),
                           # U = c("","","","1-3","1",""),
                           `R library dependencies` = Package %>%
                             purrr::map(~ {
                               utils::packageDescription(.x) %>%
                                 `[`(c("Depends", "Imports")) %>%
                                 purrr::map(~{
                                   if(is.null(.x)){
                                     character(0)
                                     }else{
                                       .x %>%
                                         strsplit(",\\n") %>%
                                         purrr::flatten_chr() %>%
                                         purrr::map(~strsplit(.x,", ") %>%
                                                      purrr::flatten_chr()) %>%
                                         purrr::flatten_chr() %>% sort() %>%
                                         purrr::discard(~startsWith(.x,"R "))
                                       }
                                   }) %>%
                                 purrr::flatten_chr() %>%
                                 unique() %>%
                                 sort() %>%
                                 purrr::map_chr(~{
                                   updated_1L_chr <- stringr::str_replace_all(.x,"\\n"," ")
                                   problem_idx_1L_chr <- stringr::str_locate(updated_1L_chr," ")[1,1] %>%
                                     unname()
                                   if(!is.na(problem_idx_1L_chr))
                                     updated_1L_chr <- updated_1L_chr %>%
                                     stringr::str_sub(end = problem_idx_1L_chr-1)
                                   updated_1L_chr %>% 
                                     trimws(which = "left") 
                                   })
                               }) %>% 
                             purrr::map_chr (~ .x %>% paste0(collapse = " "))) %>% 
  as.data.frame() 
# if(params$X@outp_formats_chr[1] != "Word"){
#       df$Ref <- c(rep("",6)
#        # "@ready42022","@ready4fun2022","@ready4class2022","@ready4pack2022","@ready4use2022","@ready4show2022"
#                   )
# }else{
#   df$Ref <- ""
# }

df <- df %>%
  # dplyr::mutate(Standard = purrr::pmap_chr(df,
  #                                          ~paste0("A",
  #                                                 ..3,
  #                                                 paste0(rep("&nbsp;",
  #                                                     2+max(nchar(df[,3]))-nchar(..3)),
  #                                                     collapse = ""#
  #                                                     ),
  #                                                 ifelse(..4=="","","R"),
  #                                                 ..4,
  #                                                 paste0(rep("&nbsp;",
  #                                                     2+max(nchar(df[,4]))-nchar(..4)),
  #                                                     collapse = ""#
  #                                                     ),
  #                                                 ifelse(..5=="","","U"),
  #                                                 ..5,
  #                                                 paste0(rep("&nbsp;",
  #                                                     1+max(nchar(df[,5]))-nchar(..5)),
  #                                                     collapse = ""#
  #                                                     )#,
  #                                                 ))) %>%

  dplyr::select(Package,
                #Ref,
                Purpose,
                #Standard,
                `R library dependencies`)

names_chr <- names(df)
# df <- data.frame(df[,1],
#                  rep(ifelse(params$X@outp_formats_chr[1] == "Word"," ","&nbsp; &nbsp; &nbsp;"),
#                      nrow(df)),
#                  df[,2#:3
#                     ],
#                  rep(ifelse(params$X@outp_formats_chr[1] == "Word"," ","&nbsp; &nbsp; &nbsp;")
#                      ,nrow(df)),
#                  #df[,4],
#                  #rep("&nbsp; &nbsp; &nbsp;",nrow(df)),
#                  df[,3#5
#                     ])
# colnames(df) <- c("Package",
#                   ifelse(params$X@outp_formats_chr[1] == "Word","XXX"," "),
#                   #"Ref", 
#                   "Purpose", 
#                   ifelse(params$X@outp_formats_chr[1] == "Word","YYY"," "),
#                   #"Standard     ",# " ",
#                   "R library dependencies")
#df$Package <- "![](../Data/images/ready4.png){ width=10% }"#"\\includegraphics[valign=T,scale=2.5,raise=2mm]{../Data/images/ready4.png}"
#df$`Standard     `  <- df$`Standard     ` %>% stringr::str_replace_all("&nbsp;"," ")
if(params$X@outp_formats_chr[1] == "Word") {
  library("flextable")
  library("ftExtra")
  df[,c(1,3:4,6:7)] %>%
    ready4show::print_table(output_type_1L_chr = params$X@outp_formats_chr[1],
                            caption_1L_chr = knitr::opts_current$get("tab.cap"),
                            mkdn_tbl_ref_1L_chr = paste0("tab:",knitr::opts_current$get("tab.id")),
                            use_rdocx_1L_lgl = ifelse(params$X@outp_formats_chr[1]=="Word",T,F),
                            add_to_row_ls = NULL,
                            sanitize_fn = NULL) %>%
    ftExtra::colformat_md()
  }else{
    #df$Ref<-NULL
    #df$Package <- ""
    df$Package  <- df$Package %>% 
                      purrr::map_chr(~paste0("\\includegraphics[valign=M,width=1.9cm,raise=4mm]{../Data/images/",.x,"_logo.png}"))#scale=0.4,raise=3mm]
    # df$Package <- "\\includegraphics[valign=M,scale=0.08,raise=3mm]{../Data/images/ready4.png}"
    #df[,c(1,3,5:6)]   %>%
    df %>%
    # kableExtra::kbl(format = "markdown",
    #                   escape = F,
    #                 caption = knitr::opts_current$get("tab.cap"))
      kableExtra::kbl(booktabs = T, 
                      escape = F,
                      caption = knitr::opts_current$get("tab.cap")) %>%
      kableExtra::kable_paper(full_width = F) %>%
      kableExtra::column_spec(2, width = "20em", latex_valign = "m") %>%
      # kableExtra::column_spec(1, 
      #                         image = kableExtra::spec_image(rep("../Data/images/ready4.png",nrow(df)), 
      #                                                           150, 150)) %>%
      kableExtra::column_spec(3, width = "20em",
                              latex_valign = "m")
    }
```
